Benchmarking of quantum processors with random circuits

### 2018-05-28 paper/main.tex
abstract and outline

@@

\begin{figure}[t]
\begin{center}
{\includegraphics[width=\columnwidth]{device.png}}
\caption{\label{device} The layout of the \emph{ibmqx3} device, with the numbering of qubits used in this study. Lines connect pairs of qubits for which a CNOT can be performed. Thick black lines are show for the CNOTs used in our implementation of the repetition code.
}
\end{center}
\end{figure}

>>>>

Quantum processors with sizes in the 10-100 qubit range are now commonplace. However, with increased size comes increased complexity for benchmarking. The effectiveness of a given device may vary greatly between different tasks, and won’t always be  easy to predict from single and two qubit gate fidelities. For this reason, it is important to assess processor quality for a range of important tasks. In this work we propose and implement tests based on random quantum circuits. These are used to evaluate four different superconducting qubit devices, with sizes from 5 to 19 qubits, from three hardware manufacturers: IBM Research, Rigetti and Alibaba.

@@

\section{Generation of random circuits}

\section{Figures of merit}

\subsection{Error mitigation}

\section{Results}

\subsection{5 and 16 qubit IBM devices}

\subsection{19 qubit Rigetti device}

\subsection{11 qubit Alibaba device}

\section{Conclusions}

%\begin{figure}[t]
%\begin{center}
%{\includegraphics[width=\columnwidth]{device.png}}
%\caption{\label{device} The layout of the \emph{ibmqx3} device, with the numbering of qubits used in this study. Lines connect pairs of qubits for which a CNOT can be performed. Thick black lines are show for the CNOTs used in our implementation of the repetition code.
%}
%\end{center}
%\end{figure}
